A Simple Type Theory for Category Theory

### 2022-02-27 paper/lipics-v2021-sample-article.tex
A missing connective?!? This should allow us to define slice/comma cats and potentially fibrations!

@@

>>>>

\subsection{Graph of a Profunctor}

One final multiplicative we can define is the \emph{graph} of a
profunctor. This is unique among the multiplicatives in that it
defines a \emph{category} rather than a profunctor. It is a negative
multiplicative but it looks like a positive ??. A functor into the
category of elements $\exists (\alpha; \beta). R$ is equivalent to a
morphism into the functor $R$.

\begin{figure}
  \begin{mathpar}
    \inferrule*[right=Graph-Formation]
    {\Gamma \vdash \alpha:\cat C; \beta:\cat D \vdash R \isaSet}
    {\Gamma \vdash \exists (\alpha;\beta). R \isaCat}

    \inferrule*[right=Graph-E+]
    {\Gamma \vdash \gamma:\cat E \vdash \phi : \exists(\alpha:\cat C;\beta: \cat D).R}
    {\Gamma \vdash \pi_+\phi : \cat C}

    \inferrule*[right=Graph-E-]
    {\Gamma \vdash \gamma:\cat E \vdash \phi : \exists(\alpha:\cat C;\beta: \cat D).R}
    {\Gamma \vdash \pi_-\phi : \cat D}

    \inferrule*[right=Graph-Ep]
    {\Gamma \vdash \gamma:\cat E \vdash \phi : \exists(\alpha:\cat C;\beta: \cat D).R}
    {\Gamma \vdash \gamma:\cat E \vdash \pi_p\phi : R[\pi_+\phi/\alpha,\pi_-\phi/\beta]}

    \inferrule*[right=Graph-Intro]
    {\Gamma\vdash \gamma:\cat E \vdash a : \cat C \and
      \Gamma\vdash \gamma:\cat E \vdash b : \cat D \and
      \Gamma\vdash \gamma:\cat E \vdash t : R[a/\alpha;b/\beta]}
    {\Gamma\vdash \gamma:\cat E \vdash (a,b,t) : \exists (\alpha;\beta). R}

    \inferrule*[right=Unit-Formation]
    {\Gamma \vdash \cat C \isaCat\and
     \Gamma \pipe d^-\Xi \vdash a_1 : \cat C\and \Gamma \pipe d^+ \Xi \vdash a_2 : \cat C}
    {\Gamma \pipe \Xi \vdash \punitinXfromYtoZ {\cat C} {a_1} {a_2}}

    \pi_+(a,b,t) = a \\
    \pi_-(a,b,t) = b \\
    \pi_p(a,b,t) = t\\

    \inferrule
    {\Gamma \vdash \gamma:\cat E \vdash \phi : \exists(\alpha:\cat C;\beta:\cat D). R}
    {\phi = (\pi_+\phi, \pi_-\phi, \pi_p\phi)}
  \end{mathpar}  
  \caption{Graph of a Profunctor}
\end{figure}

Semantically, the graph of a profunctor is simply the category of
elements of the profunctor. Taking the profunctor to be (restrictions
of) the hom profunctor allows us to define the slice, arrow and comma
categories.

@@

\paragraph{As a tool for Formal Type Theory}
